Results (Barcelona)

### 2022-02-14 docs/01_stimuli.Rmd
Render Rmds

animacy %>% 
	filter(role=="Prime") %>% 
	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
	facet_wrap(location~test_language, ncol = 4) +
	geom_col(position = position_fill(), colour = "#0D1117") +
	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
	labs(title = "Prime", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
	scale_y_continuous(labels = percent) +
	coord_flip() + 
	theme(
		axis.title.x = element_blank()
	) +

	animacy %>% 
	filter(role=="Target") %>% 
	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
	facet_wrap(location~test_language, ncol = 4) +
	geom_col(position = position_fill(), colour = "#0D1117") +
	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
	labs(title = "Target", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
	scale_y_continuous(labels = percent) +
	coord_flip() +

@@

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	pivot_longer(c(category_prime, category_target), names_to = "role", values_to = "category") %>% 
	mutate(role = str_to_sentence(str_remove(role, "category_"))) %>% 
	drop_na(trial_type, category) %>% 
	count(trial_type, test_language, location, role, category) %>% 
	ggplot(aes(n, trial_type, colour = category, fill = category, order = n)) +
	facet_wrap(role~location~test_language) +
	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
	labs(x = "% of trials", y = "Trial type",
		 colour = "Trial type", fill = "Trial type") +
	scale_x_continuous(labels = percent) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text = element_text(size = 9),
		axis.title.y = element_blank(),
		plot.caption = element_text(size = 10, hjust = 0),
		panel.grid = element_blank()

>>>>

animacy %>% 
	filter(role=="Prime") %>% 
	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
	facet_wrap(location~test_language, ncol = 4) +
	geom_col(position = position_fill()) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	labs(title = "Prime", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
	scale_y_continuous(labels = percent) +
	coord_flip() + 
	theme(
		axis.title.x = element_blank()
	) +

	animacy %>% 
	filter(role=="Target") %>% 
	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
	facet_wrap(location~test_language, ncol = 4) +
	geom_col(position = position_fill()) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	labs(title = "Target", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
	scale_y_continuous(labels = percent) +
	coord_flip() +

@@

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	pivot_longer(c(category_prime, category_target), names_to = "role", values_to = "category") %>% 
	mutate(role = str_to_sentence(str_remove(role, "category_"))) %>% 
	drop_na(trial_type, category) %>% 
	count(trial_type, test_language, location, role, category) %>% 
	ggplot(aes(n, trial_type, colour = category, fill = category, order = n)) +
	facet_wrap(role~location~test_language) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "% of trials", y = "Trial type",
		 colour = "Trial type", fill = "Trial type") +
	scale_x_continuous(labels = percent) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text = element_text(size = 9),
		axis.title.y = element_blank(),
		plot.caption = element_text(size = 10, hjust = 0),
		panel.grid = element_blank()

### 2022-02-14 docs/05_attrition.Rmd
Render Rmds

```{r participants_cdi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>%
	left_join(vocabulary) %>% 
	drop_na(valid_participant) %>% 
	mutate(
		valid_status = case_when(
			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
			!valid_participant ~ "Not valid"
		)
	) %>% 
	ggplot(aes(lp, fill = valid_status)) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = "#0D1117", size = 1) +
	geom_hline(yintercept = 24, linetype = "dashed", colour = "white") +
	scale_colour_brewer(palette = "Set1") +
	labs(x = "Group", y = "Sample size", fill = "Valid?") +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.x = element_blank(),
		panel.grid.minor.y = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) 
```

@@

attrition_location %>% 
	filter(location=="Barcelona") %>% 
	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Barcelona") +

	attrition_location %>% 
	filter(location=="Oxford") %>% 
	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Oxford") +

@@

```{r trials_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(select(participants, participant, location)) %>% 
	count(location, age_group, trial_type, valid_status) %>% 
	drop_na(trial_type) %>% 
	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
	facet_grid(location~age_group) +
	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	scale_y_continuous(labels = percent) +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid = element_blank(),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

@@

attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, frequency_target_childes) %>% 
	ggplot(aes(trial_type, frequency_target_childes, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_boxplot(fill = "#0D1117", width = 0.25,
				 position =  position_dodge(width = 0.5),
				 size = 0.75, outlier.colour = NA) +
	geom_label(data = sample_size, aes(y = 2, label = n), size = 3,
			   position = position_dodge(width = 0.7), colour = "#0D1117") +
	labs(x = "Trial type", y = "Frequency (CHILDES)", colour = "Validity", fill = "Validity") +
	scale_y_continuous(breaks = 0:7, limits = c(0, 7)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.x = element_blank(),
		panel.grid.minor.y = element_blank(),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

```{r attrition_frequency_target_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
	drop_na(trial_type, frequency_target_childes) %>% 
	mutate(frequency_target_childes = round(frequency_target_childes)) %>% 
	count(trial_type, age_group, valid_status, trial_type, frequency_target_childes) %>% 
	ggplot(aes(as.factor(frequency_target_childes), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

@@

attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, familiarity_target) %>% 
	ggplot(aes(trial_type, familiarity_target, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_boxplot(fill = "#0D1117", width = 0.25,
				 position =  position_dodge(width = 0.5),
				 size = 0.75, outlier.colour = NA) +
	geom_label(data = sample_size, aes(y = 0.1, label = n), size = 3,
			   position = position_dodge(width = 0.7), colour = "#0D1117") +
	labs(x = "Trial type", y = "Familiarity", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent, limits = c(0, 1)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.y = element_blank(),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

```{r attrition_familiarity_target_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
	drop_na(trial_type, familiarity_target) %>% 
	mutate(familiarity_target = round(familiarity_target, digits = 1)) %>% 
	count(trial_type, age_group, valid_status, trial_type, familiarity_target) %>% 
	ggplot(aes(as.factor(familiarity_target), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

@@

```{r attrition_animacy_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_target)) %>%
	mutate(is_animate_target = ifelse(is_animate_target, "Animate", "Inanimate")) %>% 
	drop_na(trial_type, is_animate_target) %>% 
	count(trial_type, age_group, valid_status, trial_type, is_animate_target) %>% 
	ggplot(aes(as.factor(is_animate_target), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)

@@

```{r attrition_category_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_target)) %>%
	drop_na(trial_type, category_target) %>% 
	count(trial_type, age_group, valid_status, trial_type, category_target) %>% 
	ggplot(aes(fct_rev(category_target), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

>>>>

```{r participants_cdi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>%
	left_join(vocabulary) %>% 
	drop_na(valid_participant) %>% 
	mutate(
		valid_status = case_when(
			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
			!valid_participant ~ "Not valid"
		)
	) %>% 
	ggplot(aes(lp, fill = valid_status)) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(size = 1) +
	geom_hline(yintercept = 24, linetype = "dashed", colour = "white") +
	scale_colour_brewer(palette = "Set1") +
	labs(x = "Group", y = "Sample size", fill = "Valid?") +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.x = element_blank(),
		panel.grid.minor.y = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) 
```

@@

attrition_location %>% 
	filter(location=="Barcelona") %>% 
	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Barcelona") +

	attrition_location %>% 
	filter(location=="Oxford") %>% 
	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Oxford") +

@@

```{r trials_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(select(participants, participant, location)) %>% 
	count(location, age_group, trial_type, valid_status) %>% 
	drop_na(trial_type) %>% 
	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
	facet_grid(location~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	scale_y_continuous(labels = percent) +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid = element_blank(),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

@@

attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, frequency_target_childes) %>% 
	ggplot(aes(trial_type, frequency_target_childes, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_boxplot(fill = "white", width = 0.25,
				 position =  position_dodge(width = 0.5),
				 size = 0.75, outlier.colour = NA) +
	geom_label(data = sample_size, aes(y = 2, label = n), size = 3,
			   position = position_dodge(width = 0.7), colour = "white") +
	labs(x = "Trial type", y = "Frequency (CHILDES)", colour = "Validity", fill = "Validity") +
	scale_y_continuous(breaks = 0:7, limits = c(0, 7)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.x = element_blank(),
		panel.grid.minor.y = element_blank(),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

```{r attrition_frequency_target_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
	drop_na(trial_type, frequency_target_childes) %>% 
	mutate(frequency_target_childes = round(frequency_target_childes)) %>% 
	count(trial_type, age_group, valid_status, trial_type, frequency_target_childes) %>% 
	ggplot(aes(as.factor(frequency_target_childes), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

@@

attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, familiarity_target) %>% 
	ggplot(aes(trial_type, familiarity_target, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_boxplot(fill = "white", width = 0.25,
				 position =  position_dodge(width = 0.5),
				 size = 0.75, outlier.colour = NA) +
	geom_label(data = sample_size, aes(y = 0.1, label = n), size = 3,
			   position = position_dodge(width = 0.7), colour = "white") +
	labs(x = "Trial type", y = "Familiarity", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent, limits = c(0, 1)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.y = element_blank(),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

```{r attrition_familiarity_target_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
	drop_na(trial_type, familiarity_target) %>% 
	mutate(familiarity_target = round(familiarity_target, digits = 1)) %>% 
	count(trial_type, age_group, valid_status, trial_type, familiarity_target) %>% 
	ggplot(aes(as.factor(familiarity_target), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

@@

```{r attrition_animacy_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_target)) %>%
	mutate(is_animate_target = ifelse(is_animate_target, "Animate", "Inanimate")) %>% 
	drop_na(trial_type, is_animate_target) %>% 
	count(trial_type, age_group, valid_status, trial_type, is_animate_target) %>% 
	ggplot(aes(as.factor(is_animate_target), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)

@@

```{r attrition_category_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_target)) %>%
	drop_na(trial_type, category_target) %>% 
	count(trial_type, age_group, valid_status, trial_type, category_target) %>% 
	ggplot(aes(fct_rev(category_target), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

### 2022-02-14 docs/06_results.Rmd
Render Rmds

model_comparison <- waics_l1 %>% 
	map("estimates") %>% 
	map(function(x) rownames_to_column(as.data.frame(x), "variable")) %>% 
	bind_rows(.id = "model") %>%
	clean_names() %>% 
	pivot_wider(names_from = variable, values_from = c(estimate, se)) %>% 
	relocate(model, matches("estimate"), matches("elpd"), matches("_p_")) %>% 
	mutate(
		model = c(
			"Intercept",
			"... + Trial type",
			"... + Group \u00d7Trial type\u00d7Group",
			"... + Vocab. + Trial type\u00d7Vocab. + Group\u00d7Vocab.",
			"... + Trial type\u00d7Vocab. + Group\u00d7Vocab. + Trial type\u00d7Group\u00d7Vocab."
		)
	) %>% 
	gt() %>% 
	fmt_number(-model) %>% 
	tab_spanner("WAIC", matches("waic")) %>% 
	tab_spanner(md("WAIC<sub>ELPD</sub>"), matches("elpd")) %>% 
	tab_spanner(md("WAIC<sub>*p*</sub>"), matches("_p_")) %>% 
	cols_label(
		model = "Model",
		estimate_elpd_waic = "Estimate",
		estimate_waic = "Estimate",
		estimate_p_waic = "Estimate",
		se_elpd_waic = md("*SE*"),
		se_waic = md("*SE*"),
		se_p_waic = md("*SE*"),
	) %>% 
	cols_align("right", "model") %>% 
	tab_style(
		cell_text(weight = "bold"),
		cells_column_spanners()
	) %>% 
	tab_style(
		cell_text(style = "italic"),
		cells_column_labels()
	)

gtsave(model_comparison, here("img", "model_comparison.png"))

as_raw_html(model_comparison)

@@

draws %>% 
	group_by(.variable, .variable_name, type) %>% 
	mean_qi() %>% 
	select(type, .variable_name, .value, .lower, .upper) %>% 
	gt(rowname_col = ".variable", groupname_col = "type")  %>% 
	fmt_percent(3) %>%
	fmt_number(4:5, scale_by = 100) %>% 
	cols_merge(c(".lower", ".upper"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		.variable_name = md("**Predictor**"),
		.value = md("**Mean**"),
		.lower = md("**95% CrI**")
	) %>% 
	tab_style(
		style = list(
			cell_text(weight = "bold", style = "italic")
		),
		locations = list(
			cells_row_groups()
		)
	) %>% 
	tab_style(
		style = list(
			cell_text(weight = "bold")
		),
		locations = list(
			cells_column_labels()
		)
	) %>% 
	as_raw_html()
```

>>>>

# model_comparison <- waics_l1 %>% 
# 	map("estimates") %>% 
# 	map(function(x) rownames_to_column(as.data.frame(x), "variable")) %>% 
# 	bind_rows(.id = "model") %>%
# 	clean_names() 
# 	pivot_wider(names_from = variable, values_from = c(estimate, se)) %>% 
# 	relocate(model, matches("estimate"), matches("elpd"), matches("_p_")) %>% 
# 	mutate(
# 		model = c(
# 			"Intercept",
# 			"... + Trial type",
# 			"... + Group \u00d7Trial type\u00d7Group",
# 			"... + Vocab. + Trial type\u00d7Vocab. + Group\u00d7Vocab.",
# 			"... + Trial type\u00d7Vocab. + Group\u00d7Vocab. + Trial type\u00d7Group\u00d7Vocab."
# 		)
# 	) %>% 
# 	gt() %>% 
# 	fmt_number(-model) %>% 
# 	tab_spanner("WAIC", matches("waic")) %>% 
# 	tab_spanner(md("WAIC<sub>ELPD</sub>"), matches("elpd")) %>% 
# 	tab_spanner(md("WAIC<sub>*p*</sub>"), matches("_p_")) %>% 
# 	cols_label(
# 		model = "Model",
# 		estimate_elpd_waic = "Estimate",
# 		estimate_waic = "Estimate",
# 		estimate_p_waic = "Estimate",
# 		se_elpd_waic = md("*SE*"),
# 		se_waic = md("*SE*"),
# 		se_p_waic = md("*SE*"),
# 	) %>% 
# 	cols_align("right", "model") %>% 
# 	tab_style(
# 		cell_text(weight = "bold"),
# 		cells_column_spanners()
# 	) %>% 
# 	tab_style(
# 		cell_text(style = "italic"),
# 		cells_column_labels()
# 	)
# 
# gtsave(model_comparison, here("img", "model_comparison.png"))
# 
# 
# as_raw_html(model_comparison)

@@

draws %>% 
	group_by(.variable, .variable_name, type) %>% 
	mean_qi() %>% 
	select(type, .variable_name, .value, .lower, .upper) %>% 
	gt(rowname_col = ".variable", groupname_col = "type")  %>% 
	fmt_percent(3) %>%
	fmt_number(4:5, scale_by = 100) %>% 
	cols_merge(c(".lower", ".upper"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		.variable_name = md("**Predictor**"),
		.value = md("**Mean**"),
		.lower = md("**95% CrI**")
	) %>% 
	tab_style(
		cell_text(weight = "bold", style = "italic"),
		cells_row_groups()
	) %>% 
	as_raw_html()
```
